Fractional anisotropy as a tracer of cosmic voids

### 2014-09-24 cosmic_voids.tex
Rewriting and streamlining FA as a tracer of voids subsection

Here we introduce a new tracer of the structure of cosmic voids built from 
two tensorial web schemes, i.e. the T-web, based on the Hessian of the 
gravitational potential or tidal tensor \citep{Hahn07, Forero09}, and the 
V-web, based on the velocity shear tensor \citep{Hoffman12}. These web 
schemes classify the Cosmic Web into four different types of environment
depending on the counting of the number of eigenvalues below an 
user-defined threshold ($\lambda_{th}$), namely voids (3 eigenvalues below
$\lambda_{th}$), sheets (2), filaments (1) and knots or clusters (0).
The tidal and the shear tensors have proven to be more fundamental than 
the density field as they also trace the collapsing or expanding nature of 
the matter field, which ultimately is what defines the underlying dynamics 
of the Cosmic Web. Furthermore, the density field is degenerated regarding 
the defined types of environment \citep{Hahn07}, which implies that is not 
possible to assign a priori a range of density values to each of them. 
This yields that the usually adopted definition of voids as simply 
underdense regions in the large-scale matter distribution, is not precise 
enough as it excludes a proper description of the internal structure of 
voids.

Following the recent trend of using digital image-processing techniques 
developed in other disciplines (e.g. medical sciences and computer imaging) 
for analysing the structure of the Cosmic Web, we propose here, much in 
the same way as \citet{Libeskind13}, the fractional anisotropy (FA) as a 
tracer of the internal structure and the outline of cosmic voids. The FA 
was initially introduced by \citet{Basser95} for quantifying the 
anisotropy degree of the diffusivity of water molecules through cerebral
tissue in nuclear magnetic resonance imaging. In this context we use the 
same quantity for determining the anisotropy degree of the local 
environment from either the orbital dynamics as set by the eigenvalues of
the tidal tensor (T-web), or the dynamics of the velocity field as set by 
the eigenvalues of the shear tensor (V-web). In both cases, the FA is not
determined directly from the density field, it hence is suitable for 
describing both, the structure of high non-linear regions (e.g. filaments,
knots and very dense walls) as well as the fainter substructure exhibited 
by quasi-linear regions like voids.

@@

This paper is organized as follows. In section 2 we describe the used
simulation for testing our void finding algorithm, i.e. the Bolshoi
simulation. Alternatively to the web schemes T-web and V-web, we propose 
a heuristic web classifier based on three thresholds of the density field. 
This is used in order to illustrate the differences of our scheme with a
density-based classifier. A detailed description of these methods is 
presented in section 3. In section 4 we describe how the FA can be used 
for tracing the structure of voids. Once obtained meaningful catalogues 
of voids for each scheme, we proceed to compare some typical and general 
interest properties of voids such as volume functions, distributions of 
size and density and velocity profiles. This is done in section 5. Finally 
in section 6 we analyse and evaluate our findings.

@@

%-------------------------------------------------------------------------
\subsection{The tidal web (T-web)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\subsection{The velocity web (V-web)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematical scheme to define the Cosmic Web environment in 
the simulation. The scheme has been thoroughly described in 
\citet{Hoffman12} and applied to study the shape and spin alignment in the
Bolshoi simulation in \citet{Libeskind13}. We refer the reader to these 
papers to find a detailed description of the algorithm, its limitations 
and capabilities. The V-web scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. The central quantity is given by the 
following dimensionless expression

@@

In the same way, the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ allows for the local 
classification of the matter distribution into the previous four web types. 
For the threshold choosing in both schemes, the V-web and the T-web, it is
usual to fine-tuning the value in such a way that the visual appearance of
the Cosmic Web as seen in simulations and galaxy surveys is reproduced. 
However, we do not take this approach here, instead we propose a novel 
approach for the threshold choosing based on the maximization of the 
fractional anisotropy field occurring in filaments and very dense walls.

@@

Although the density field is a key quantity for understanding the 
large-scale Universe, the filamentary structure of the Cosmic Web is 
poorly traced by it (see e.g. figure \ref{fig:FA_field}). In order to 
compare our new proposal based on the the fractional anisotropy as a 
tracer field of voids, we define a very basic approach for environmental 
finding based on three thresholds of the density field.

%.........................................................................
%Table with volume filling fraction
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{c  c  c  c c} \hline\hline
	\textbf{Volume}  &				&\textbf{Scheme}& \\
	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
	\textbf{Fraction}&\textbf{T-web}&\textbf{V-web}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
	Sheets		     &	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	      &	$0.60$				\\
	Filaments		 &	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 		  &	$8.82$				\\
	Knots			 &	$0.75\%$	&	$1.22\%$	&	$0.98\%$  		  &	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small VFF for each type of environment and for each
  web scheme. VFF for the density-based scheme are defined as the 
  arithmetic mean of the T-web and the V-web. The last column corresponds 
  to the threshold values in the density field in order to obtain the 
  required VFF. Note there is not any value associated to knots as there 
  is not a higher order environment.}

@@

In next section we shall describe an alternative approximation to select 
the threshold value $\lambda_{th}$. One of the main results is the similar 
volume filling fraction (VFF) for each environment in both web schemes. 
Using this result, we propose here a heuristic classification of the 
Cosmic Web based on three density thresholds assigned to each boundary 
(i.e. void-sheet, sheet-filament and filament-knot)\footnote{The 
progressive sequence void-sheet-filament-knot along any path through the 
Cosmic Web should be always satisfied as each used field is smoothed.} 
such that the corresponding VFF values are similar to the values obtained 
for the T-web and the V-web, specifically they are defined to be the 
arithmetic mean of both schemes.

%*************************************************************************
\section{Finding bulk voids}
\label{sec:bulk_voids}
%*************************************************************************

@@

%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} } }
%.........................................................................
where the eigenvalues are taken from either the T-web or the V-web 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
corresponds with a isotropic dynamic and $FA=1$ with a highly anisotropic 
distribution.

In the figure \ref{fig:FA_field} we calculate the FA field over the 
simulation for both web schemes. The first interesting feature of this
figure is the degeneration presented for knots and central regions of 
voids, where both of them exhibit low to middle values of the FA, 
indicating a high isotropy regarding the physical properties quantified by 
each web scheme, i.e. the density field for the T-web and the peculiar 
velocity for the V-web. For the T-web, the FA field near to knots presents 
a very narrow distribution around a local minimum, whereas for the V-web 
such distribution is more spread out. This can be explained appealing to 
the low fluctuations of the density field compared with the peculiar 
velocity in highly non-linear regions like knots. For more linear regions 
like voids, the behaviour of the FA field is quite similar between both 
schemes, what is consistent with the equivalence of the T-web and the 
V-web in the linear regime \SRKED{[reference, Hoffman]}.

According to the classification scheme adopted for the cosmological 
environment, voids are regions where 
$\lambda_3\leq\lambda_2\leq\lambda_1\leq\lambda_{th}$. This implies that
the boundaries of void regions are controlled completely by the $\lambda_1$
eigenvalue of the web scheme and the threshold value. Therefore, as we 
increase the threshold value $\lambda_{th}$, all voids grow up 
progressively through contours of the $\lambda_1$ field until certain 
critical value where they are so large that the visual impression is no 
longer reproduced. Our objective here is to find a reliable quantity that 
allows to trace the geometry of void regions as classified by each web 
scheme. In the figure \ref{fig:L1_correlations} we calculate the 
distributions of the fractional anisotropy index and the density field 
regarding the $\lambda_1$ eigenvalue for both web schemes over all the 
cells of the simulation. Thick lines correspond to the median of the 
distributions, whereas coloured regions correspond to $50\%$ of the
sample, delimited by quartiles $Q_1$ and $Q_3$.

The first important conclusion is regarding the distribution of the FA 
index, where there is an almost perfect correlation with the $\lambda_1$ 
eigenvalue for low values of it. This result can be interpreted as an 
one-dimensional tomography of void regions, where low $\lambda_1$ values 
are associated to the central regions of voids, these being the most 
isotropic structures found, with FA values close to 0. As we increase the 
$\lambda_1$ value, corresponding to progressively outer layers of void 
regions or less isotropic voids, the FA index increases as well, 
maintaining a very reliable correlation approximately until $FA=0.95$. 
This limit value of the FA can be traduced in terms of an optimal \lth, 
where we obtain $\lambda_{opt}^V = 0.175$ for the V-web scheme and 
$\lambda_{opt}^T = 0.265$ for the T-web scheme, both values consistent 
with optimal thresholds normally taken in previous works \SRKED{[references]}. 
Due to the definition of the fractional anisotropy index, it presents the 
highest values for filaments and very flat sheets, i.e. $FA\lesssim 1$.
Therefore, if we extend the $\lambda_{th}$ value beyond the optimal 
FA limit, such that the outer regions of voids becomes highly anisotropic, 
it would imply that voids are invading filaments and sheets, so the 
optimal \lth value is a limit value up to which we can have void regions. 
For other type of environment such as sheets, filaments and knots, the 
$\lambda_1$ eigenvalue does not control their spatial boundaries, so the 
correlation with the FA index is no longer valid beyond the threshold 
values, furthermore the larger dispersion of the FA distribution also 
indicates that contours of the FA field are no longer corresponding to 
contours of the $\lambda_1$ field. Nevertheless, for high $\lambda_1$ 
values, i.e. $\lambda_1>1.0$, the median value of the FA index decreases 
to lower values, indicating the presence of isotropic knots. All of this 
allows us to conclude that the distribution of the FA with respect to the 
$\lambda_1$ eigenvalue is not only an one-dimensional tomography of voids, 
but also a sort of one-dimensional projection of the global structure of 
the cosmic web, starting in highly isotropic central voids, passing 
through very anisotropic sheets and filaments, until isotropic knot 
regions.

For the distribution of the density with respect to the $\lambda_1$ 
eigenvalue, it can be appreciated an analogous behaviour, where central 
regions of voids present the most underdense values of the overall cosmic 
web. For outer layers of voids, the density field grows progressively 
until sheets and filaments are reached. However, the dispersion in the 
distributions indicates that the geometry of voids as quantified by both 
web schemes is not compatible with the density field, i.e. contours of the
$\lambda_1$ eigenvalue do not coincide with contours of the density field. 
Then, the density is not a reliable quantity to be used as tracer of our 
voids. Furthermore, another advantage of using the FA index instead of the
density is the non-monotonous behaviour of the FA median value, with a 
local maxima that allows to identify properly the boundaries of voids.

@@

Resuming our endeavour at identifying voids in cosmological simulations, 
previous techniques based on web classification schemes usually perform a 
FOF-like algorithm over cells previously marked as voids according to some 
established criteria in order to construct bulk void regions 
\SRKED{[references]}. Although this method has some success at classifying 
voids, percolation is completely inevitable, where the only way to reduce 
it is artificially decreasing the global volume fraction of void regions 
such that they do not merge significantly each other.

Once has been determined the reliability of the FA index for tracing 
the geometry of voids, our novel proposal here is rather using the FA 
field for classifying void regions. As was concluded in the previous 
subsection, the geometry of voids is completely traced by contours of the
FA field, where central parts of voids and high density knot regions 
exhibit particularly low values of the FA index. Therefore, through a 
watershed transform all voids are classified, where each single void 
region corresponds to the basin of a local minimum of the FA field, where
those local minimums are restricted to be embedded into a type-void cell
in order to avoid degeneracy with knots.

@@

%.........................................................................
%FIGURE 1: Distributions of FA and density regarding the Lambda_1 eigenvalue
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

  \captionof{figure}{\small Volume Filling Fraction for each type of 
  environment with respect to the chosen threshold $\lambda_{th}$ for both
  web schemes (T-web, left panel. V-web, right panel). For each case, the 
  threshold value is chosen such that the fractional anisotropy along the 
  void-sheet boundaries has a value of $FA=0.95$.}

@@

  \captionof{figure}{\small Distributions of fractional anisotropy 
  (left panel) and density field (right panel) with respect to the 
  eigenvalue $\lambda_1$ for each web scheme (T-web, red lines. V-web, 
  blue lines) as calculated over all cells of the grid. Thick central 
  lines correspond to the median and filled regions to the $50\%$ of 
  the distribution.}

@@

@@

>>>>

Here we introduce a new tracer of the structure of cosmic voids built from 
two tensorial web schemes, i.e. the Tweb, based on the Hessian of the 
gravitational potential or tidal tensor \citep{Hahn07, Forero09}, and the 
Vweb, based on the velocity shear tensor \citep{Hoffman12}. These web 
schemes classify the Cosmic Web into four different types of environment
depending on the counting of the number of eigenvalues below an 
user-defined threshold ($\lambda_{th}$), namely voids (3 eigenvalues below
$\lambda_{th}$), sheets (2), filaments (1) and knots or clusters (0).
The tidal and the shear tensors have proven to be more fundamental than 
the density field as they also trace the collapsing or expanding nature of 
the matter field, which ultimately is what defines the underlying dynamics 
of the Cosmic Web. Furthermore, the density field is degenerated regarding 
the defined types of environment \citep{Hahn07}, which implies that is not 
possible to assign a priori a range of density values to each of them. 
This yields that the usually adopted definition of voids as simply 
underdense regions in the large-scale matter distribution, is not precise 
enough as it excludes a proper description of the internal structure of 
voids.

Following the recent trend of using digital image-processing techniques 
developed in other disciplines (e.g. medical sciences and computer imaging) 
for analysing the structure of the Cosmic Web, we propose here, much in 
the same way as \citet{Libeskind13}, the fractional anisotropy (FA) as a 
tracer of the internal structure and the outline of cosmic voids. The FA 
was initially introduced by \citet{Basser95} for quantifying the 
anisotropy degree of the diffusivity of water molecules through cerebral
tissue in nuclear magnetic resonance imaging. In this context we use the 
same quantity for determining the anisotropy degree of the local 
environment from either the orbital dynamics as set by the eigenvalues of
the tidal tensor (Tweb), or the dynamics of the velocity field as set by 
the eigenvalues of the shear tensor (Vweb). In both cases, the FA is not
determined directly from the density field, it hence is suitable for 
describing both, the structure of high non-linear regions (e.g. filaments,
knots and very dense walls) as well as the fainter substructure exhibited 
by quasi-linear regions like voids.

@@

This paper is organized as follows. In section 2 we describe the used
simulation for testing our void finding algorithm, i.e. the Bolshoi
simulation. Alternatively to the web schemes Tweb and Vweb, we propose 
a heuristic web classifier based on three thresholds of the density field. 
This is used in order to illustrate the differences of our scheme with a
density-based classifier. A detailed description of these methods is 
presented in section 3. In section 4 we describe how the FA can be used 
for tracing the structure of voids. Once obtained meaningful catalogues 
of voids for each scheme, we proceed to compare some typical and general 
interest properties of voids such as volume functions, distributions of 
size and density and velocity profiles. This is done in section 5. Finally 
in section 6 we analyse and evaluate our findings.

@@

%-------------------------------------------------------------------------
\subsection{The tidal web (Tweb)}
\label{subsec:Tweb}
%-------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\subsection{The velocity web (Vweb)}
\label{subsec:Vweb}
%-------------------------------------------------------------------------

We also use a kinematical scheme to define the Cosmic Web environment in 
the simulation. The scheme has been thoroughly described in 
\citet{Hoffman12} and applied to study the shape and spin alignment in the
Bolshoi simulation in \citet{Libeskind13}. We refer the reader to these 
papers to find a detailed description of the algorithm, its limitations 
and capabilities. The Vweb scheme for environment finding is based on the
local velocity shear tensor calculated from the smoothed dark matter 
velocity field in the simulation. The central quantity is given by the 
following dimensionless expression

@@

In the same way, the relative strength of the three eigenvalues with 
respect to a threshold value $\lambda_{th}$ allows for the local 
classification of the matter distribution into the previous four web types. 
For the threshold choosing in both schemes, the Tweb and the Vweb, it is
usual to fine-tuning the value in such a way that the visual appearance of
the Cosmic Web as seen in simulations and galaxy surveys is reproduced. 
However, we do not take this approach here, instead we propose a novel 
approach for the threshold choosing based on the maximization of the 
fractional anisotropy field occurring in filaments and very dense walls.

@@

Although the density field is a key quantity for understanding the 
large-scale Universe, the filamentary structure of the Cosmic Web is 
poorly traced by it (see e.g. Fig. \ref{fig:FA_field}). In order to 
compare our new proposal based on the the fractional anisotropy as a 
tracer field of voids, we define a very basic approach for environmental 
finding based on three thresholds of the density field.

%.........................................................................
%Table with volume filling fraction
\begin{table}[h]
\begin{flushleft}
\begin{center}
  \begin{tabular}{c  c  c  c c} \hline\hline
	\textbf{Volume}  &				&\textbf{Scheme}& \\
	\textbf{Filling} &				&				&					  &  \textbf{Threshold} \\ 
	\textbf{Fraction}&\textbf{Tweb}&\textbf{Vweb}	&	\textbf{Density}  &  $\bf{\delta_{th}}$  \\ \hline
	Voids			 &	$54.88\%$	&	$47.06\%$	&	$50.97\%$	 	  &	$ -0.57$			\\ 
	Sheets		     &	$33.21\%$	&	$39.54\%$	&	$36.38\%$ 	      &	$0.60$				\\
	Filaments		 &	$11.16\%$	&	$12.18\%$	&	$11.67\%$ 		  &	$8.82$				\\
	Knots			 &	$0.75\%$	&	$1.22\%$	&	$0.98\%$  		  &	--		\\ \hline\hline
  \end{tabular}  
  \captionof{table}{\small VFF for each type of environment and for each
  web scheme. VFF for the density-based scheme are defined as the 
  arithmetic mean of the Tweb and the Vweb. The last column corresponds 
  to the threshold values in the density field in order to obtain the 
  required VFF. Note there is not any value associated to knots as there 
  is not a higher order environment.}

@@

In next section we shall describe an alternative approximation to select 
the threshold value $\lambda_{th}$. One of the main results is the similar 
volume filling fraction (VFF) for each environment in both web schemes 
(see Fig. \ref{fig:VFF}). Using this result, we propose here a heuristic 
classification of the Cosmic Web based on three density thresholds 
assigned to each boundary (i.e. void-sheet, sheet-filament and 
filament-knot)\footnote{The progressive sequence void-sheet-filament-knot 
along any path through the Cosmic Web should be always satisfied as each 
used field is smoothed.} such that the corresponding VFF values are 
similar to the values obtained for the Tweb and the Vweb, specifically 
they are defined to be the arithmetic mean of both schemes.

%*************************************************************************
\section{Finding voids}
\label{sec:bulk_voids}
%*************************************************************************

@@

%.........................................................................
%Fractional anisotropy
\eq{fractional_anisotropy}
{ FA = \frac{1}{\sqrt{3}}\sqrt{ \frac{ (\lambda_1 - \lambda_3)^2 + 
(\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{ \lambda_1^2 + 
\lambda_2^2 + \lambda_3^2} } }
%.........................................................................
where the eigenvalues are taken from either the Tweb or the Vweb 
(FA-Tweb and FA-Vweb respectively). Such as it is defined, $FA=0$ 
corresponds with a isotropic dynamic and $FA=1$ with a highly anisotropic 
distribution.

In left panels of Fig. \ref{fig:FA_field} we calculate the FA for both 
web schemes and the logarithmic density field over a slide of the 
simulation. Some important points can be concluded of this figure.

%.........................................................................
\begin{itemize}
\item Voids display a highly isotropic expanding dynamic at their centres, 
becoming gradually more anisotropic at outer regions.
\item Knots feature with very isotropic collapses. For the Tweb, the FA 
exhibits very narrow distribution around knots whereas for the Vweb, these
distributions are more spread out, thereby indicating strong differences 
between the density and the velocity fields in highly non-linear regions.
\item The filamentary structure of the Cosmic Web is very good traced by
high FA values (black regions), thus indicating very anisotropic dynamics 
for sheets and filaments.
\item The density field poorly traces the Cosmic Web. This is a somehow 
expected result due to the semi-infinite range of the density field, what 
makes more difficult to trace structures.
\end{itemize}
%.........................................................................

Some of these results are consistent with those of \citet{Libeskind13}.
Finally, from Fig. \ref{fig:FA_field} we conclude that the FA, unlike the
density field, displays a non-monotonic behaviour, where low values are 
characteristic of central regions of voids, reaching high values in sheets
and filaments and becoming low again in knots.

For both web schemes, voids are regions where $\lambda_3\leq\lambda_2\leq
\lambda_1\leq\lambda_{th}$. This implies that the outlines of voids
are completely fixed by the relative strength of the $\lambda_1$ 
eigenvalue with respect to the threshold value. Therefore, as we 
increase/decrease the threshold value $\lambda_{th}$, voids expand/diminish
progressively through contours of $\lambda_1$. In Fig. 
\ref{fig:L1_correlations} we calculate the distribution of the FA as well
as of the density field with respect to $\lambda_1$ for both web schemes 
over all cells of the simulation.

From Fig. \ref{fig:L1_correlations} we conclude that the FA is a good
tracer of voids as is perfectly correlated with low values of $\lambda_1$. 
Then, it reaches a maximum value, namely sheets and filaments, for finally
reaching knots, which feature low FA values. This behaviour can be thought 
as a sort of one-dimensional tomography of the Cosmic Web. This 
characteristic allows us to propose an optimal threshold value for both 
web schemes where the FA is maximized. Specifically we propose a value of 
$FA=0.95$, corresponding with a threshold $\lambda_{opt}^T = 0.265$ for
the Tweb and $\lambda_{opt}^V = 0.175$ for the Vweb.  For a threshold 
above these values, voids would span over very anisotropic regions, which 
should correspond to sheets and filaments. A threshold below would imply 
very low volume filling fractions of voids and dominant sheets. Finally 
from the same figure, the density field do not correlate well with 
$\lambda_1$ (as calculated for both web schemes). Moreover, due to its 
monotonic increase, an estimate of a optimal threshold is not as clear as 
for the FA.

Once set the optimal thresholds for the web schemes, we proceed in Fig. 
\ref{fig:FAShapeness} to sample the FA along with the prolatenes for a 
random sample of cells classified into the four environments. Then, we 
associate a spheroidal geometry with different ranges of these properties
in order to illustrate the underlying local dynamics of the sampled cells.

From this figure we conclude that sheets displays, as expected, very 
anisotropic distributions, namely above $FA=0.95$. They are also biased 
towards oblate geometries, however there are some elongated sheets as 
well. Filaments are not as anisotropic as sheets, ranging from middle up 
to high FA values. They exhibit prolate geometries, but a considerable 
amount of them are biased towards slightly more oblate values. Voids and 
knots are the only environments featuring with low FA values, thus 
indicating very isotropic expanding/collapsing dynamics at their centres. 
However, voids span over a very wide range of FA and geometries, whereas 
knots only span over low to middle FA values and display a biased oblate 
geometry.

@@

@@

%.........................................................................
%FIGURE 1: Volume Filling Fractions for environs
\begin{flushleft}
\begin{figure*}
\centering
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Tweb.pdf}
  \includegraphics[trim = 2mm 2mm 5mm 6mm, clip, keepaspectratio=true,
  width=0.3\textheight]{./figures/cosmicweb_volume_Vweb.pdf}

  \captionof{figure}{\small Volume Filling Fraction for each type of 
  environment with respect to the chosen threshold $\lambda_{th}$ for both
  web schemes (Tweb, left panel. Vweb, right panel). For each case, the 
  threshold value is chosen such that the fractional anisotropy along the 
  void-sheet boundaries has a median value of $FA=0.95$.}

@@

  \captionof{figure}{\small Distributions of the fractional anisotropy 
  (left panel) and the density field (right panel) with respect to the 
  eigenvalue $\lambda_1$ for each web scheme (Tweb, red lines. Vweb, 
  blue lines) as calculated over all cells of the grid. Thick central 
  lines correspond with the median and filled regions with the $50\%$ of
  the distribution.}

@@

  \label{fig:FAShapeness}
  \vspace{0.1 cm}

@@

  \label{fig:RhoVel}
  \vspace{0.1 cm}
